Reproducible workflow on a public cloud for computational fluid dynamics

### 2019-03-18 tex/MesnardoBarba2019.tex
add abstract

>>>>

\IEEEtitleabstractindextext{%
\begin{abstract}
In a new effort to make our research transparent and reproducible by others, we have developed a workflow to run computational studies on a public cloud. It uses Docker containers to create an image of the application software stack. We also adopt several tools that facilitate creating and managing virtual machines with compute nodes and submitting jobs to these nodes. The configuration files for these tools are part of an expanded "reproducibility package" that includes workflow definitions for cloud computing, in addition to input files and instructions. This facilitates re-creating the cloud environment to re-un the simulations under the same conditions.
\end{abstract}
}
